A basis for selecting the spectral photon flux density distribution of light for measuring leaf photosynthetic rates in light quality response studies

### 2016-08-13 Header.Rmd
微修正など。

---
title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
csl: ECB.csl
bibliography: ~/GitHub/BeeLabR/BibTex/With.bib
header-includes:
  - \setmainfont{Times New Roman}
  # - \setmainfont{Helvetica Neue}
  - \usepackage{zxjatype} # 日本語を使うためのパッケージ
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォントの指定
  - \usepackage{lscape} # 図を回転するためのパッケージ
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節ためのパッケージ
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
  - \usepackage{lineno} # 行番号を追加するためのパッケージ
  - \linenumbers # 行番号を追加する

output:
#   pdf_document:
#     latex_engine: xelatex
#     fig_caption: TRUE
# fontsize: 20pt
# geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  word_document:
    toc: FALSE
    fig_caption: TRUE
---

>>>>

---
title: "A basis for selecting the spectral photon flux density distribution of light for measuring leaf photosynthetic rates in light quality response studies"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
csl: ECB.csl
bibliography: ~/GitHub/BeeLabR/BibTex/With.bib
header-includes:
  - \setmainfont{Times New Roman}
  # - \setmainfont{Helvetica Neue}
  - \usepackage{zxjatype} # 日本語を使うためのパッケージ
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォントの指定
  - \usepackage{lscape} # 図を回転するためのパッケージ
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節ためのパッケージ
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
  - \usepackage{lineno} # 行番号を追加するためのパッケージ
  - \linenumbers # 行番号を追加する

output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: TRUE
fontsize: 20pt
geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  # word_document:
  #   toc: FALSE
  #   fig_caption: TRUE
---
